Create data sets for modeling

### 2016-07-14 portfolio/analysis/3-createData_linear_modeling.Rmd
Add missing line

codes$description <- gsub(", VESSEL OVER 80", " VESSEL OVER 80", codes$description)
codes$description <- gsub(";97m", "", codes$description)
codes$description <- gsub(", VESSEL PERMIT OVER 80", " VESSEL PERMIT OVER 80", codes$description)
codes$description <- gsub(", VESSEL PERMIT TO 80", " VESSEL PERMIT TO 80", codes$description)
reg <- "([A-Za-z0-9/&(). -]+),([A-Za-z0-9()%/&.' -]+),([A-Za-z0-9/&.' ,()-]+)"
codes$pfshy_species <- tolower(gsub(reg, "\\1", codes$description))
codes$pfshy_gear <- tolower(gsub(reg, "\\2", codes$description))
codes$pfshy_area <- tolower(gsub(reg, "\\3", codes$description))
codes$pfshy_species <- sub(" +$", "", codes$pfshy_species)
readr::write_csv(codes, path = "../data-generated/cfec-codes.csv")
# as.data.frame(codes)
```
## Identify most popular strategies by person-year combination

>>>>

codes$description <- gsub(", VESSEL OVER 80", " VESSEL OVER 80", codes$description)
codes$description <- gsub(";97m", "", codes$description)
codes$description <- gsub(", VESSEL PERMIT OVER 80", " VESSEL PERMIT OVER 80", codes$description)
codes$description <- gsub(", VESSEL PERMIT TO 80", " VESSEL PERMIT TO 80", codes$description)
reg <- "([A-Za-z0-9/&(). -]+),([A-Za-z0-9()%/&.' -]+),([A-Za-z0-9/&.' ,()-]+)"
codes$pfshy_species <- tolower(gsub(reg, "\\1", codes$description))
codes$pfshy_gear <- tolower(gsub(reg, "\\2", codes$description))
codes$pfshy_area <- tolower(gsub(reg, "\\3", codes$description))
codes$pfshy_species <- sub(" +$", "", codes$pfshy_species)
readr::write_csv(codes, path = "../data-generated/cfec-codes.csv")
# as.data.frame(codes)
```

## Identify most popular strategies by person-year combination
